Barneby Lives!

### 2023-05-11 scripts/taxonomy_setup.Rmd
spepecies spell check support for infraspecies, and formatted output results

```{r}
library(tidyverse)
library(kewr)
library(WorldFlora)
WFO.remember()
source('functions.R')
```

@@

```{r}

cla <- data.table::fread('../taxonomic_data/WFO_Backbone/classification.txt')
genLKPtab <- unique(cla, by = 'genus')[taxonomicStatus == 'Accepted','genus'] %>% 
  arrange(genus) %>% 
  mutate(Grp = str_extract(genus, '[A-Z][a-z]{1}'))%>% 
  rename(strings = genus)

speLKPtab <- unique(cla, by = 'specificEpithet')[
  taxonomicStatus == 'Accepted','specificEpithet'] %>% 
  arrange(specificEpithet) %>% 
  mutate(Grp = str_extract(specificEpithet, '[a-z]{3}')) %>% 
  rename(strings = specificEpithet)

spell_check('Poa annua') # works
spell_check('Poar annua') # works
spell_check('Poa annur') # works
spell_check('Poar annur') # works
spell_check('Pou annua') # works

@@

stages...
verify the spelling of the genus (parse these from the POWO webshot)
verify the spelling of the epithet (parse these from the POWO webshot)

if not verified
fuzzy match genus... (somehow get a local list.....)
fuzzy match epithet...

find authorship...

>>>>

```{r}
library(tidyverse)
library(kewr)
library(WorldFlora)
# WFO.remember()
source('functions.R')
```

@@

```{r prepare materials for look up tables, eval = F}

cla <- data.table::fread('../taxonomic_data/WFO_Backbone/classification.txt', na.strings = "")

epiLKPtab <- cla[, c('scientificName', 'specificEpithet', 'infraspecificEpithet', 'verbatimTaxonRank')]
epiLKPtab <- filter(epiLKPtab, is.na(verbatimTaxonRank) | verbatimTaxonRank != "f.")

genLKPtab <- unique(cla, by = 'genus')[taxonomicStatus == 'Accepted','genus'] %>% 
  arrange(genus) %>% 
  mutate(Grp = str_extract(genus, '[A-Z][a-z]{1}'))%>% 
  rename(strings = genus)
speLKPtab <- unique(cla, by = 'specificEpithet')[
  taxonomicStatus == 'Accepted','specificEpithet'] %>% 
  arrange(specificEpithet) %>% 
  mutate(Grp = str_extract(specificEpithet, '[a-z]{3}')) %>% 
  rename(strings = specificEpithet)

spell_check('Penstemon scariosus var. garrettii') # works
spell_check('Penstemen scariosus var. garrettii') # works
spell_check('Penstemen scariosius var garratti') # works
spell_check('Penstemen scariosius ssp garratti') # works
spell_check('Penstemen scariosus') # works

@@
